### 2010-06-08 docs/architecture/architecture.tex
update docs to reflect new Makefile organization

The next set of lines tell the build system where to look for source
files.  A MAESTRO application is built from several pacakges (the
multigrid solver, an EOS, a reaction network, etc.).  
\begin{verbatim}
  FPARALLEL := ../..

  include $(FPARALLEL)/mk/GMakedefs.mak

  Fmdirs := boxlib \
            mg \
            MAESTRO \
            extern/EOS/helmeos \
            extern/EOS/conducteos \
            extern/constants \
            extern/networks/ignition \
            extern/VODE

  Fmincludes := extern/EOS/helmeos
\end{verbatim}
The {\tt FPARALLEL} variable should point to the top-level directory
of the source tree (i.e.\ {\tt fParallel/}).  Next we include the
compiler definitions, {\tt mk/GMakedefs.mak}.  The {\tt Fmdirs}
variable lists the individual directories in the {\tt fParallel/}
source tree that are used to build the problem.  Generally, one does
not need to include the problem directory itself, unless there are
unique source files found there, described in a {\tt GPackage.mak}
file.  The build system will attempt to build all of the files listed
in the various {\tt GPackage.mak} files found in the {\tt Fmdirs}
directories.  Furthermore, {\tt Fmdirs} will be will be added to the
{\tt make} {\tt VPATH}, which is the list of directories to search for
source files.  The problem directory will always be put first in the
{\tt VPATH}, so any source files placed there override those with the
same name found elsewhere in the source tree.  The {\tt Fmincludes}
variable lists all those directories that contain include files that
are inserted into the Fortran source at compile time via the {\tt
  include} statement.  Presently, the only instance of this is with
the Helmholtz general equation of state found in {\tt
  extern/EOS/helmeos/}.

>>>>

The next two lines define where the top of the source tree is
include the basic Makefile information (like compiler
flags).
\begin{verbatim}
  FPARALLEL := ../..

  include $(FPARALLEL)/mk/GMakedefs.mak
\end{verbatim}

A MAESTRO application is built from several pacakges (the
multigrid solver, an EOS, a reaction network, etc.).  The core
MAESTRO packages are always included, so a problem only needs
to define the EOS, reaction network, and conductivities to
use, as well as any extra, problem specific files.  
\begin{verbatim}
EOS_DIR := extern/EOS/helmeos   
CONDUCTIVITY_DIR := extern/EOS/conducteos 
NETWORK_DIR := extern/networks/ignition_chamulak

EXTRA_DIR := extern/random
\end{verbatim}
Generally, one does not need to include the problem directory itself
in {\tt EXTRA\_DIR}, unless there are unique source files found there,
described in a {\tt GPackage.mak} file.  These variables are
interpreted by the {\tt GMaestro.mak} file and used to build a master
list of packages called {\tt Fmdirs}.  The build system will attempt
to build all of the files listed in the various {\tt GPackage.mak}
files found in the {\tt Fmdirs} directories.  Furthermore, {\tt
  Fmdirs} will be will be added to the {\tt make} {\tt VPATH}, which
is the list of directories to search for source files.  The problem
directory will always be put first in the {\tt VPATH}, so any source
files placed there override those with the same name found elsewhere
in the source tree.  Some packages (for instance, the {\tt helmeos}
EOS) require Fortran include files.  The {\tt Fmincludes} variable
lists all those directories that contain include files that are
inserted into the Fortran source at compile time via the {\tt include}
statement.  Presently, the only instance of this is with the Helmholtz
general equation of state found in {\tt extern/EOS/helmeos/}.  This is
automatically handled by the {\tt GMaestro.mak} instructions.
